A large-scale analysis of racial disparities in police stops across the United

### 2019-12-05 lib/paper_results.Rmd
adding std error to pfs

```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

@@

```{r search_rates}
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

>>>>

```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_annual_stop_rate = mean(annual_stop_rate),
    std_error = sqrt(var(annual_stop_rate) / length(annual_stop_rate)),
    CI_lower = average_annual_stop_rate - 1.96 * std_error,
    CI_upper = average_annual_stop_rate + 1.96 * std_error
  ) %>%
  kable()
```

@@

```{r search_rates}
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_search_rate = mean(search_rate),
    std_error = sqrt(var(search_rate) / length(search_rate)),
    CI_lower = average_search_rate - 1.96 * std_error,
    CI_upper = average_search_rate + 1.96 * std_error
  ) %>%
  kable()
```
